---
title: "Food Web Project Test Markdown"
author: "Jennings"
date: "10/27/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Read in raw data
```Raw_Data_2019_July<- read.csv("~/S.Fk.McKenzie_FoodWeb_Study/DataRaw/SFMR_Wisseman_Long_Aggregate_Output_2019_July.csv")
Raw_Data_2019_October<- read.csv("~/S.Fk.McKenzie_FoodWeb_Study/DataRaw/SFMR_Wisseman_Long_Aggregate_Output_2019_October.csv")
```
## Adds A Column named "Season" to each seasonal data set

```
Season <- rep("Summer",length(Raw_Data_2019_July$Date))
Raw_Data_2019_July$Season<- cbind(Season)
Season <- rep("Fall",length(Raw_Data_2019_October$Date))
Raw_Data_2019_October$Season<- cbind(Season)

## Rbind the dataframes together
```
CombRawDat_2019<- rbind(Raw_Data_2019_July,Raw_Data_2019_October)
```

## Coerce the dates from factor to date in the "Date" column
```
class(CombRawDat_2019$Date)
CombRawDat_2019$Date<- as.Date(CombRawDat_2019$Date, format="%Y-%m-%d")
class(CombRawDat_2019$Date)
```
## Removes the columns: Waterbody, Higher.classification,Common.name, Abundance  
```
CombRawDat_2019<- CombRawDat_2019[,-c(1,10,13,14)]
```
## Subset by: 
- Treatment(Treatment = Site)
- Substrate (Benthic, Submerged Wood), 
- Stage
- Insect
```
Disturbed_BenthInsect_Data_2019<- subset(CombRawDat_2019, Treatment=="Disturbed" & Substrate=="Benthic" & Insect=="insect" & Stage=="L")
Flooded_Forest_BenthInsect_Data_2019<- subset(CombRawDat_2019, Treatment=="Flooded Forest" & Insect=="insect" & Stage=="L") ##Only benthic substrate was sampled
Relic_Channel_BenthInsect_Data_2019<- subset(CombRawDat_2019, Treatment=="Relic Floodplain Channel" & Substrate=="Benthic" & Insect=="insect" & Stage=="L")
Phase3_BenthInsect_Data_2019<- subset(CombRawDat_2019, Treatment=="Phase 3" & Insect=="insect" & Stage=="L") ##Only benthic substrate was sampled in Phase3
Phase4_BenthInsect_Data_2019<- subset(CombRawDat_2019, Treatment=="Phase 4" & Insect=="insect" & Stage=="L") ##Only benthic substrate was sampled in Phase4
Disturbed_WoodInsect_Data_2019<- subset(CombRawDat_2019, Treatment=="Disturbed" & Substrate=="Submerged Wood" & Insect=="insect" & Stage=="L")
Relic_Channel_WoodInsect_Data_2019<- subset(CombRawDat_2019, Treatment=="Relic Floodplain Channel" & Substrate=="Submerged Wood" & Insect=="insect" & Stage=="L")
```
```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
